Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-03-30 parts/figures.tex

\begin{figure*}
\includegraphics[width=\linewidth]{img/mlens_vs_mstel_one/mstel_vs_mtot_one}
\caption{Total mass in the model against the estimated stellar mass,
  alongside the values for the whole sample.  (The labelled orange
  bars are the systems shown in detail in
  Figures~\ref{fig:splinput}--\ref{fig:encl}.)  The horizontal and
  vertical extents of each bar indicate the uncertainties in the
  stellar and total masses.  The lower-right shaded region is
  unphysical according to the stellar-population models, because it
  gives $M<\Mstel$. The upper-left shaded region is unphysical
  according to abundance matching (see Section~\ref{sec:stellar-mass})
  because it gives $M>\Mhalo$.  That is to say, the unshaded region is
  $0<\haloindex<1$. \label{fig:stelmass}}
\end{figure*}

>>>>

\begin{figure*}
\includegraphics[width=\linewidth]{img/mlens_vs_mstel_one/mstel_vs_mtot_one}
\caption{Total mass in the model against the estimated stellar mass,
  alongside the values for the whole sample.  (The labelled orange
  bars are the systems shown in detail in
  Figures~\ref{fig:splinput}--\ref{fig:encl}.)
  The horizontal extend of each bar indicates the uncertainties in the stellar
  mass, esitmated assuming a ``young'' and ``old'' age trend
  for the population synthesis models; whereas the vertical extents indicade
  the spread of total halo mass in one ensemble of models.
  The lower-right shaded region is
  unphysical according to the stellar-population models, because it
  gives $M<\Mstel$. The upper-left shaded region is unphysical
  according to abundance matching (see Section~\ref{sec:stellar-mass})
  because it gives $M>\Mhalo$.  That is to say, the unshaded region is
  $0<\haloindex<1$. \label{fig:stelmass}}
\end{figure*}
